Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-06-05 manuscript/manuscript.Rmd
WIP

>>>>

Significant differences exist between process configurations (Friedman test: $p < 10^{-5})$.

# Convert to data matrix. First aggregate within each experiment because the
# Wilcoxon signed rank test is not for repeated measurements.
data <- data.table::dcast(
  data,
  dataset ~ learner + transformation_method + normalisation_method, value.var="value_rank",
  fun.aggregate = mean
)

data[, "dataset" := NULL]
configurations <- colnames(data)
```

Something about direct comparisons.

To assess the marginal effects of process parameters, including transformation method, we first fit a regression random forest (ranger package [@Wright2017-rf] (version 0.16.0); 2000 trees, minimum node size 2, other hyperparameters default) with process parameters and task difficulty as predictors and normalised rank as response variable.
